%==============================================================
%  Ziqiu Zeng — Curriculum Vitae  (source of truth)
%  Compile:  make            (needs a LaTeX engine, see README)
%       or:  pdflatex cv.tex
%       or:  tectonic cv.tex
%  Standard pdfLaTeX. No exotic packages -> also builds on Overleaf.
%==============================================================
\documentclass[11pt,a4paper]{article}

% ---------- packages ----------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}

% ---------- edit-me: personal details ----------
\newcommand{\myname}{Ziqiu Zeng}
\newcommand{\myrole}{Research Manager (Simulation Lead), Human-Centered Robotics Lab}
\newcommand{\myaffil}{National University of Singapore}
\newcommand{\myemail}{zzeng@nus.edu.sg}
\newcommand{\myhomepage}{https://ziqiu-zeng.github.io/homepage}
\newcommand{\myscholar}{https://scholar.google.com/citations?user=u7adOeQAAAAJ&hl=en}

% bold my own name in author lists
\newcommand{\me}{\textbf{Ziqiu Zeng}}

\hypersetup{
  pdftitle={\myname{} - Curriculum Vitae},
  pdfauthor={\myname},
  colorlinks=true,
  urlcolor=blue!55!black,
}

% ---------- section styling: small caps + full-width rule ----------
\titleformat{\section}
  {\normalfont\large\scshape}{}{0em}{}
  [\vspace{-0.45em}\rule{\linewidth}{0.6pt}]
\titlespacing*{\section}{0pt}{1.15em}{0.55em}

% ---------- helpers ----------
% one row: flowing left text + right-aligned date
\newcommand{\daterow}[2]{%
  \noindent\begin{tabularx}{\linewidth}{@{}X r@{}}#1 & #2\end{tabularx}\par}

\newlist{pubs}{enumerate}{1}
\setlist[pubs]{leftmargin=1.7em,itemsep=0.4em,topsep=0.3em,label=\arabic*.}

\setlist[itemize]{leftmargin=1.4em,itemsep=0.32em,topsep=0.3em}
\setlength{\parindent}{0pt}

%==============================================================
\begin{document}

% ---------- header ----------
\begin{center}
  {\LARGE\scshape \myname}\\[0.45em]
  \myrole\\
  \myaffil\\[0.35em]
  \href{mailto:\myemail}{\myemail} \quad|\quad
  \href{\myhomepage}{Homepage} \quad|\quad
  \href{\myscholar}{Google Scholar}
\end{center}
\vspace{0.3em}

% ---------- employment ----------
\section{Employment History}
\daterow{\textbf{National University of Singapore}, Research Fellow}{2025 -- present}
\daterow{\textbf{CAIR-CAS, Hong Kong}, Research Fellow}{2023 -- 2025}

% ---------- education ----------
\section{Academic Qualifications}
\daterow{\textbf{Ph.D. in Computer Graphics}, University of Strasbourg, France}{2019 -- 2023}
\daterow{\textbf{Eng. Degree in Automation}, University of Technology of Troyes, France}{2017 -- 2019}
\daterow{\textbf{B.Sc. in Computer Science}, University of Shanghai, China}{2013 -- 2017}

% ---------- interests ----------
\section{Research Interest}
Physics Engines for Robotics, Contact Mechanics, Differentiable Simulation,
GPU Numerical Architecture, Sim-to-Real for Manipulation.

% ---------- publications ----------
\section{Selected Related Research Publications}
\begin{pubs}
  \item \me, et al. Fast But Accurate: A Real-Time Hyperelastic Simulator with
        Robust Frictional Contact. \textit{ACM Transactions on Graphics (Proc.\ ACM SIGGRAPH 2025)}.
  \item \me, et al. Fast and Reliable Gradients for Deformables Across Frictional
        Contact Regimes. arXiv:2603.16478 (2026).
  \item Siyuan Luo, \ldots, \me\textsuperscript{*}, Fan Shi. FLASH: Fast Learning via
        GPU-Accelerated Simulation for High-Fidelity Deformable Manipulation in Minutes.
        arXiv:2604.17513 (2026).
  \item \me, et al. Real-Time FE Simulation for Large-Scale Problems using
        Precondition-Based Contact Resolution and Isolated DOFs Constraints.
        \textit{Computer Graphics Forum 2022}.
  \item \me, et al. Dynamic Cutting Simulation using Elastic Snapping for Mesh
        Quality Optimization. \textit{Computer Graphics Forum 2025}.
  \item Zhenhao Huang, \ldots, \me, Fan Shi. Few-Shot Neural Differentiable Simulator:
        Real-to-Sim Rigid-Contact Modeling. \textit{IEEE ICRA 2026}.
  \item Xin Liu, \ldots, \me, \ldots, Fan Shi. Enabling Robust Cloth Manipulation via
        Inference-Time Simulator-in-the-Loop Refinement. arXiv:2606.24552 (2026).
  \item Chunzheng Wang, \ldots, \me, \ldots, Fan Shi. Soft Responsive Materials Enhance
        Humanoid Safety. arXiv:2601.02857 (2026).
\end{pubs}
\vspace{0.2em}
{\footnotesize \textsuperscript{*}\,Corresponding author.}

% ---------- grants ----------
\section{Grants \& Research Funding}
\begin{itemize}
  \item \textbf{NVIDIA Academic Grant}, 2025. \textit{Adaptive Fault-Tolerant Safe Locomotion with Differentiable Simulation}.
  \item \textbf{Google Research Funding}, 2025. \textit{Sim-to-Dex: Contact-Rich Graph Neural Models for Robotic Manipulation}.
  \item \textbf{Swiss AI Initiative Small Grant}, 2025. \textit{Learning Deformable Contact Dynamics for 4D Spatial Intelligence}.
\end{itemize}

% ---------- talks / posters / service ----------
\section{Invited Talks, Posters \& Service}
\begin{itemize}
  \item \textbf{Talks \& Workshops:} ETH Zurich CRL Seminar; IEEE ICRA 2025; CoRL 2025.
  \item \textbf{Posters:} ACM SIGGRAPH Asia 2025; NUS AI Research Day; RAS TC Model-Based Optimization for Robotics (2025).
  \item \textbf{Service:} Organizer, IEEE ICRA 2026 Workshop ``Synthetic Data for Robot Learning''.
\end{itemize}

\end{document}
